251 MA

### 2023-03-01 code/process.Rmd
final checks on stuff before running first model

  select(target_lastauthor_year, status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
         same_dir,
         replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code, adjudicated_replication_code)

@@

d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()
```
We have maybe as many as 177 at least for some analyses.

@@

- "complete" -- it's a full case

- "adj" -- will be a full case once we get subjective replication and subfield coded

- "beta" -- don't have standardized ES, but have a pair that we can do predInt to

- "ES_direction" -- we don't have the direction coded (ex. is an interaction that I can't eyeball, or a multi-way F test with no graph)

@@

- "done" -- got as far as I can, and that is that we have demographics but not stats

@@

- "reproduction" -- student did a reproduction and not replication 
-->

@@

# d_val$academic_year |> unique()
# 
# d_val |> filter(!subfield %in% c("social","cognitive","non-psych","other-psych"))
# 
# d_val |> filter(!stanford_internal %in% c("no","yes"))
# 
# d_val |> filter(!open_data %in% c("no","yes"))
# 
# d_val |> filter(!open_materials %in% c("no","yes"))
# 
# d_val |> filter(!target_on_turk %in% c("no","yes"))
# 
# d_val |> filter(!replication_on_turk %in% c("no","yes"))
# 
# d_val |> filter(!within_between %in% c("within","between","mixed"))
# 
# d_val |> filter(!single_vignette %in% c(0,1))

@@

}

#pool_m_sd(2.875,1.3102163,16,3.5,.8548504,14)
#pool_m_sd(1.5, 1.6329932, 16, 2.25, 1.6583124, 12)
#pool_m_sd(2.48,1.41,46,3.35,1.07,49)
#pool_m_sd(1.90,1.54,49,2.22,1.46,49)
```
# Parsing

@@

est_SE <- function(p,d){
  z <- -.862+sqrt(abs(.743-2.404*log(p)))
  SE <- abs(d/z)
  return(SE)
}

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df)
    N_from_df=df+1
  }
  se=est_SE(pval, d_calc)
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
    se=est_SE(pval,d_calc)
  }
  else if(!is.na(df_1)){
    # we go through partial eta
    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
    #partial_eta=(val*df_1)/(val*df_1+df_2)
    #d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
    d_calc=NA
    se=NA
  }

@@

```{r}
parse_mean_ci <- function(mci,within_between,n){
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  sd_pool=(sd1+sd2)/2
  se=sd_pool/sqrt(n)
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
}

@@

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
}

@@

```{r}
fill_es <- function(type, value, n){
  if (is.na(type)) {
    return(NA)}
  if (is.na(value)) {
    return(NA)
  }
  if (type=="partial eta sq"){
    d = sqrt( (n-1)/n * abs(value)/(1-abs(value)))
    return(d)
    }
  if (type %in% c("d", "SMD")){
    return(abs(value))
  }
  return(NA)
}

test <- d_val |> 
  mutate(target_raw_stat=gsub(" ","",target_raw_stat),
         target=pmap(list(target_raw_stat, within_between,target_N), do_parsing),
         replication_raw_stat=gsub(" ","",replication_raw_stat),
         rep=pmap(list(replication_raw_stat, within_between,replication_N), do_parsing)) |> 
  unnest(cols=c(target, rep), names_sep="_") |> 
  rowwise() |> 
  mutate(d_fill_target=fill_es(target_ES_type, target_ES_value, target_N),
         d_fill_rep=fill_es(replication_ES_type, replication_ES_value, replication_N))

```
<!--
## Compare pvals

Comparing calculated p vals to provided (or hand calculated) ones. Line is x=y.

These look pretty reasonable. Lots on the line and others is places were <.001's happened.

It may be worth checking points that are above the line.

@@

ggplot(test, aes(x=target_pvalue, y=target_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+
  scale_x_log10()+scale_y_log10()

ggplot(test, aes(x=replication_pvalue, y=rep_p_calc))+geom_point()+geom_abline(slope=1,intercept=0)+scale_x_log10()+scale_y_log10()

@@

## Compare ES

Comparing calculated ES to original (or hand calculated) ES. All converted to SMD.

Note: black line is y=x, red line is y=2x. Things on y=2x probably had issues where one of the tests calculated it as (within|between) and the other did it the other way.

@@

test |> 
  ggplot(aes(x=d_fill_target, y=target_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")+coord_cartesian(xlim=c(0,5),ylim=c(0,5))+geom_abline(slope=.5,intercept=0, color="red")

test |> 
  ggplot(aes(x=d_fill_rep, y=rep_d_calc))+geom_point()+geom_abline(slope=1,intercept=0)+geom_abline(slope=2,intercept=0, color="red")+geom_abline(slope=.5,intercept=0, color="red")

Where there's a difference, I could check whether it's being compared to something *I* calculated versus something that an original paper or students paper calculated? Except that there's sources for errors in any of those. Ones where we get an off  by two error -- should I double check within-betweeness for the test? 
-->
## what didn't parse

these are ones where we did not get a non-NA effect size. Could be due to formulas being incomplete, or missing information.

note that we also aren't including the betas where we know we can't get effect size, but we'll still get porig and predInt.

test |> filter(is.na(target_d_calc)&is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)

test |> filter(is.na(rep_d_calc)&is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
```

<!--
## how are the df's lining up with sample size?

We can try to back out effective sample size from the df's. Note that we don't always expect them to agree (Welch's t test, repeated measures, comparisons only on a sample), but still useful to look at.

There's a lot of off by 1 or 2 things, which I'm unsure what to make of. (As much as possible both sample size and test stats are taken from the papers directly)

```{r}
 test |> filter(!is.na(target_N_calc)) |> select(target_N_calc, target_N, target_raw_stat, within_between, target_lastauthor_year) |>
  mutate(diff=target_N_calc-target_N) |> 
  ggplot(aes(x=target_N, y=target_N_calc, color=(target_N==target_N_calc)))+geom_point()+geom_abline(slope=1, intercept=0)+scale_y_log10()+scale_x_log10()+scale_color_manual(values=c("TRUE"="black","FALSE"="red"))

 test |> filter(!is.na(rep_N_calc)) |> select(rep_N_calc, replication_N, replication_raw_stat, within_between, target_lastauthor_year) |> mutate(diff=rep_N_calc-replication_N) |> 
   ggplot(aes(x=replication_N, y=rep_N_calc, color=(replication_N==rep_N_calc)))+geom_point()+geom_abline(slope=1, intercept=0)+scale_y_log10()+scale_x_log10()+scale_color_manual(values=c("TRUE"="black","FALSE"="red"))

```
-->
# PredInt and P_orig

@@

do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
  if (is.na(replicated_report_code)){return(as.numeric(NA))}
  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
  return(as.numeric(NA))
}
d_es_predInt <- d_es |> 
         mutate(
           predInt=do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
           p_orig=do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
           sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))

@@

@@

d_es_predInt |> mutate(p_sig=p_orig<.05) |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=p_sig))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="P_orig<.05", x="Original SMD", y="Replication SMD")

@@

# d_es_predInt |> ggplot(aes(x=replicated_report_code, y=p_orig))+geom_jitter(height=0, alpha=.5)+
#   #scale_y_log10()+
#   geom_hline(yintercept=.05)
# 
# d_es_predInt |> ggplot(aes(x=replicated_report_code, y=predInt))+geom_jitter(alpha=.5)
```

# Prelim analysis -- Correlation between ES

There's that one ling paper with ES of 10+...

Might want to just hide that point or something instead...

Could weight by precision or something

d_es |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=as.factor(replicated_report_code)))+
  geom_point()+
  #coord_cartesian(xlim=c(0,5), ylim=c(-1,5))+
  geom_abline(slope=1, intercept=0)+
    geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)

d_es |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=as.factor(replicated_report_code)))+
  geom_point()+
  coord_cartesian(xlim=c(0,5), ylim=c(-1,4))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="Replicated?", x="Original SMD", y="Replication SMD")
```

@@

message("number of NAs per column")

d_check_nas <- d_es_predInt |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
    select(target_lastauthor_year, status, academic_year, subfield, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N,
           target_p_calc, target_d_calc, rep_p_calc, rep_d_calc,
           predInt, p_orig, sub_rep)

d_check_nas |> summarize(across(everything(),~sum(is.na(.)))) |>
pivot_longer(everything()) |>
  arrange((value)) |>
  filter(value!=0)

@@

d_check_nas |> filter(across(everything(), ~!is.na(.))) |> nrow()

d_check_nas |> select(target_lastauthor_year, status, academic_year,  target_year,
                      sub_rep, subfield,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N) |> filter(if_any(everything(), ~is.na(.))) #|> nrow()

message("number of rows for predInt/p_orig w/ demographic/experimental")

d_check_nas |> select(target_lastauthor_year, status, academic_year, target_year,
                      sub_rep, subfield,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig) |>  filter(across(everything(), ~!is.na(.))) |> nrow()
```

```{r}
# papers where we don't have everything

#d_check_nas |> filter(if_any(everything(), ~is.na(.)))

#d_check_nas |> filter(across(everything(), ~!is.na(.)))

# d_check_nas  |> select(target_lastauthor_year, status, academic_year, target_year,
#            stanford_internal,open_data, open_materials, target_on_turk,
#            replication_on_turk, within_between, single_vignette, repeated_measure,
#            target_N, replication_N, predInt, p_orig) |>  filter(if_any(everything(), ~is.na(.)))
```

>>>>

  select(target_lastauthor_year, sensitivity, include,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_test, target_raw_stat, target_pvalue, target_ES_type, target_ES_value,
         same_dir,
         replication_N, replication_test, replication_raw_stat, replication_pvalue, replication_ES_type, replication_ES_value,
         replicated_instructor_code, replicated_report_code, adjudicated_replication_code)

@@

d |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> tally()

d |> group_by(include) |> tally()

```
We have maybe as many as 177 at least for some analyses.

@@

- "done" -- fully coded, can be used for whatever is specified in other column

- "ES_direction" -- we don't have the direction coded

@@

@@

- "reproduction" -- student did a reproduction and not replication

@@

@@

}
```
# Parsing

@@

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df+2)) # this is a simplification for equal groups
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df+1)
    N_from_df=df+1
  }
  se=4/N_from_df+d_calc**2/(2*N_from_df)
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(N_from_df) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
   se=4/N_from_df+d_calc**2/(2*N_from_df)
  }
  else if(!is.na(df_1)){
    d_calc=NA
    se=NA
  }

@@

```{r}
parse_mean_ci <- function(mci,within_between,n){
  # parsing 
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  # calculations 
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  per_group_n=ifelse(within_between=="within",n, n/2)
  sd1=se1*sqrt(per_group_n-1) # assume equal groups
  sd2=se2*sqrt(per_group_n-1)
  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
  se_pool=sd_pool/sqrt(n-1)
  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
  tval=(m1-m2)/se_pool |> abs()
  df=ifelse(within_between=="within", n-1, n-2)
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  #
  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
  se_pool=sd_pool/sqrt(n-1)
  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
  tval=(m1-m2)/se_pool |> abs()
  df=ifelse(within_between=="within", n-1, n-2)
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
}

@@

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()

  per_group_n=ifelse(within_between=="within",n, n/2)
  sd1=se1*sqrt(per_group_n-1) # assume equal groups
  sd2=se2*sqrt(per_group_n-1)
  sd_pool=sqrt((sd1**2+sd2**2)/2) # assume equal groups
  se_pool=sd_pool/sqrt(n-1)
  d_calc=abs(m1-m2/sd_pool) # note we force all positive and then fix later 
  tval=(m1-m2)/se_pool |> abs()
  df=ifelse(within_between=="within", n-1, n-2)
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se_pool))
}

@@

@@

test <- d_val |> 
  mutate(target_raw_stat=gsub(" ","",target_raw_stat),
         target=pmap(list(target_raw_stat, within_between,target_N), do_parsing),
         replication_raw_stat=gsub(" ","",replication_raw_stat),
         rep=pmap(list(replication_raw_stat, within_between,replication_N), do_parsing)) |> 
  unnest(cols=c(target, rep), names_sep="_") |> 
  rowwise()

@@

## what didn't parse

Check that nothing that has a stat input and doesn't get an ES out.

@@

test |> filter(is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)

test |> filter(is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
```

# PredInt and P_orig

@@

do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
  if (is.na(replicated_report_code)){return(as.numeric(NA))}
  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
  return(as.numeric(NA))
}
d_es_predInt <- d_es |> 
  rowwise() |> 
         mutate(
           predInt=do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
           p_orig=do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
           sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))

@@

# viz SMD
```{r}

@@

@@

d_es_predInt |> ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+
  geom_point()+
  coord_cartesian(xlim=c(0,2), ylim=c(-1,3))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="subrep", x="Original SMD", y="Replication SMD")

```
# viz ES any scale 
```{r}
library(ggstance)
d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=p_orig))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
    geom_point()+
  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original ES", y="Replication ES")

d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=p_orig))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
    geom_point()+
  coord_cartesian(xlim=c(-1,2), ylim=c(-1,2))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="p_orig", x="Original ES", y="Replication ES")

d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=predInt))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
    geom_point()+
  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="predInt", x="Original ES", y="Replication ES")

d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=predInt))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
    geom_point()+
  coord_cartesian(xlim=c(-1,2), ylim=c(-1,2))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=T, direction=-1)+
  labs(color="predInt", x="Original ES", y="Replication ES")

d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=sub_rep))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
    geom_point()+
  coord_cartesian(xlim=c(-1,12), ylim=c(-1,12))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="sub rep", x="Original ES", y="Replication ES")

d_es_predInt |> ggplot(aes(x=target_ES, 
                           xmin=target_ES-target_SE*1.96,
                           xmax=target_ES+target_SE*1.96, 
                           y=rep_ES,
                           ymin=rep_ES-rep_SE*1.96,
                           ymax=rep_ES+rep_SE*1.96,
                           color=sub_rep))+
  geom_linerange(alpha=.5)+
  geom_linerangeh(alpha=.5)+
    geom_point()+
  coord_cartesian(xlim=c(-1,2), ylim=c(-1,2))+
  geom_abline(slope=1, intercept=0)+
  geom_hline(yintercept=0)+
  scale_color_viridis(discrete=F, direction=-1)+
  labs(color="sub rep", x="Original ES", y="Replication ES")
```

@@

d_check_nas <- d_es_predInt |> filter(!status %in% c("missing", "non-experiment", "reproduction")) |> ungroup() |>
    select(include, target_lastauthor_year, status, academic_year, subfield, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N,
           target_p_calc, target_d_calc, rep_p_calc, rep_d_calc,
           predInt, p_orig, sub_rep)

message("expected")
d_check_nas |> filter(include %in% c("stats", "pred_int", "exp")) |> nrow()
message("actual")

d_check_nas |> filter(include %in% c("stats", "pred_int", "exp")) |>
  select(target_lastauthor_year, status, academic_year,  target_year,
                      sub_rep, subfield,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N) |> filter(across(everything(), ~!is.na(.))) |> nrow()

message("number of rows for predInt/p_orig w/ demographic/experimental")
message("expected")
d_check_nas |> filter(include %in% c("stats", "pred_int")) |> nrow()
message("actual")

d_check_nas |> filter(include %in% c("stats", "pred_int")) |>  select(target_lastauthor_year, status, academic_year, target_year,
                      sub_rep, subfield,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig) |> 
 # filter(if_any(everything(), ~is.na(.)))
  filter(across(everything(), ~!is.na(.))) |> nrow()

@@

message("expected")
d_check_nas |> filter(include %in% c("stats")) |> nrow()
message("actual")

d_check_nas |> filter(include %in% c("stats")) |> filter(across(everything(), ~!is.na(.))) |> nrow()
```
